How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-03-19 tse-paper/content.tex
Add survey description protocol

First, we filtered out articles based on 1) their title and 2) the
contextual information Google Scholar displayed. Our strategy was to
err on the side of caution, that is rather including a paper than
not. We then unified the search results, removing duplicates. After
this process, we were left with 271 (17\%) of the original search
results.

@@

This section presents the answers to our research questions:
\begin{simplebox}{Research Questions}
\begin{itemize}
 \item[\textbf{RQ1:}] Which criteria influence the suitability of a chunk retrieval technique for CI build logs?
  \item[\textbf{RQ2:}] Under which conditions are PBE, CTS, and KWS suited to retrieve information from CI build logs?

>>>>

First, we filtered out articles based on 1) their title and 2) the
contextual information Google Scholar displayed. We inlcuded only
publications written in a language intelligible to the authors (that
is, English or German), but only disregarded fewer than 1\% of search
hits due to this criterion. Our strategy was to err on the side of
caution, that is rather including a paper than not. We then unified
the results of the four search queries based on the link as the
identifying element, removing 60 articles that appeared in more than
one search query. We noticed that some publishers (ACM, Springer,
Google Books) augment a link to an article with a cutomized ID, which
specifies the link source ({\tt casa\_token, oid}). We automatically
removed it to find all true duplicates. After this process, we were
left with 259 (17\%) of the original search results.

@@

This section presents the answers to our research questions:
\begin{simplebox}{Research Questions}
\begin{itemize}  
  \item[\textbf{RQ1:}] Which build log analysis techniques exist?
  \item[\textbf{RQ2:}] Which criteria influence the suitability of a chunk retrieval technique for build logs?
